\documentclass[handout]{ximera}

\title{Post Video Questions}

\begin{document}

\begin{abstract}
\end{abstract}

%Video: Intro to Approximating Speed %Calculus Video 1

\maketitle

Please answer each of these questions to the best of your ability. You are welcome to re-watch parts of any of the videos to help you.

\begin{problem}
\item Suppose Jason is sailing his boat straight across a lake at a constant rate of 0.12 meters/second.
\begin{enumerate}
\item Let $\Delta t$ represent a change in the number of seconds elapsed during some part of Jason’s ride and let $\Delta d$ represent the corresponding change in the number of meters Jason traveled. Write an equation that expresses the relationship between $\Delta t$ and $\Delta d$. (If you use a decimal approximation, include at least 2 decimal places. You may also enter your answer unsimplified, like 1+2.)

$\Delta t = \answer{1/0.12} \times \Delta d$

\item Jason passes an island while traveling at this constant rate. At 10:30 AM, Jason is 3 meters past the island. At what time did Jason pass the island? (Fill in the hour in the first block and the minutes in the second block.)
$\answer{10}:\answer{29}$
\end{enumerate}
\end{problem}

\begin{problem}
Imagine you are driving on the highway and vary your speed to maintain a constant fuel efficiency. Select the choices to complete the statement to most accurately capture what it means to drive with a constant fuel economy: For \_\_\_\_ \_\_\_\_\_, the \_\_\_\_ is \_\_\_\_.

\begin{tabular}{l l l l l l l}

For \ \ \ &

\begin{minipage}[t]{0.2\textwidth}
\begin{multipleChoice}
\choice[correct]{fixed}
\choice{increasing}
\choice{decreasing}
\end{multipleChoice}
\end{minipage} &

\begin{minipage}[t]{0.2\textwidth}
\begin{multipleChoice}
\choice{gallons}
\choice{distance}
\choice[correct]{amount of change in gallons}
\choice{amount of change in distance}
\end{multipleChoice}
\end{minipage} &

\ \ \ the \ \ \ &

\begin{minipage}[t]{0.2\textwidth}
\begin{multipleChoice}
\choice[correct]{gallons}
\choice{distance}
\choice{amount of change in gallons}
\choice[correct]{amount of change in distance}
\end{multipleChoice}
\end{minipage} &

\ \ \ is \ \ \ &

\begin{minipage}[t]{0.2\textwidth}
\begin{multipleChoice}
\choice[correct]{constant}
\choice{increasing}
\choice{decreasing}
\end{multipleChoice}
\end{minipage}

\\
\end{tabular}

\end{problem}

\begin{problem}
Suppose $x$ and $y$ represent the measures of two quantities and $y$ changes at a constant rate of $-0.9$ with respect to $x$. As $x$ changes from 7 to 9.5, how much does $y$ change?
$\answer{-2.25}$
\end{problem}


\end{document}